Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2017-08-16 Papers/2013/ArXiv/GodProof-Abstract.tex
Update arXiv abstract

@@

%\footnotesize
\bibliographystyle{plain}
%\bibliography{Bibliography}
\begin{thebibliography}{10}

\bibitem{Adams}
R.M. Adams.
\newblock Introductory note to *1970.
\newblock In {\em {Kurt G\"odel: Collected Works Vol. 3: Unpublished Essays and
  Letters}}. Oxford University Press, 1995.

\bibitem{AndersonGettings}
A.C. Anderson and M.~Gettings.
\newblock G\"odel ontological proof revisited.
\newblock In {\em {G\"odel'96: Logical Foundations of Mathematics, Computer
  Science, and Physics: Lecture Notes in Logic 6}}. {Springer}, 1996.

\bibitem{B9}
C.~Benzm{\"u}ller and L.C. Paulson.
\newblock Exploring properties of normal multimodal logics in simple type
  theory with {LEO-II}.
\newblock In {\em {Festschrift in Honor of {Peter B. Andrews} on His 70th
  Birthday}}, pages 386--406. College Publications.

\bibitem{J23}
C.~Benzm{\"u}ller and L.C. Paulson.
\newblock Quantified multimodal logics in simple type theory.
\newblock {\em Logica Universalis (Special Issue on Multimodal Logics)},
  7(1):7--20, 2013.

\bibitem{LEO-II}
C.~Benzm{\"u}ller, F.~Theiss, L.~Paulson, and A.~Fietzke.
\newblock {LEO-II} - a cooperative automatic theorem prover for higher-order
  logic.
\newblock In {\em Proc. of IJCAR 2008}, volume 5195 of {\em LNAI}, pages
  162--170. Springer, 2008.

\bibitem{Coq}
Y.~Bertot and P.~Casteran.
\newblock {\em {Interactive Theorem Proving and Program Development}}.
\newblock Springer, 2004.

\bibitem{Sledgehammer}
J.C. Blanchette, S.~B\"ohme, and L.C. Paulson.
\newblock Extending {Sledgehammer} with {SMT} solvers.
\newblock {\em Journal of Automated Reasoning}, 51(1):109--128, 2013.

\bibitem{Nitpick}
J.C. Blanchette and T.~Nipkow.
\newblock Nitpick: A counterexample generator for higher-order logic based on a
  relational model finder.
\newblock In {\em Proc. of ITP 2010}, number 6172 in LNCS, pages 131--146.
  Springer, 2010.

\bibitem{Satallax}
C.E. Brown.
\newblock Satallax: An automated higher-order prover.
\newblock In {\em Proc. of IJCAR 2012}, number 7364 in LNAI, pages 111 -- 117.
  Springer, 2012.

\bibitem{ContemporaryBibliography}
R.~Corazzon.
\newblock Contemporary bibligraphy on the ontological proof
  (\url{http://www.ontology.co/biblio/ontological-proof-contemporary-biblio.htm}).

\bibitem{Fitting}
M.~Fitting.
\newblock {\em {Types, Tableaux and G\"odel's God}}.
\newblock Kluver Academic Press, 2002.

\bibitem{Goedel1970}
K.~G\"odel.
\newblock Ontological proof.
\newblock In {\em {Kurt G\"odel: Collected Works Vol. 3: Unpublished Essays and
  Letters}}. Oxford University Press, 1970.

\bibitem{GoedelNotes}
K.~G\"odel.
\newblock {\em Appendix A. Notes in Kurt G\"odel's Hand}, pages 144--145.
\newblock In  \cite{sobel2004logic}, 2004.

\bibitem{Hazen}
A.P. Hazen.
\newblock On g\"odel's ontological proof.
\newblock {\em Australasian Journal of Philosophy}, 76:361--377, 1998.

\bibitem{Hurd03first-orderproof}
J.~Hurd.
\newblock First-order proof tactics in higher-order logic theorem provers.
\newblock In {\em Design and Application of Strategies/Tactics in Higher Order
  Logics, NASA Tech. Rep. NASA/CP-2003-212448}, 2003.

\bibitem{Isabelle}
T.~Nipkow, L.C. Paulson, and M.~Wenzel.
\newblock {\em {Isabelle/HOL: A Proof Assistant for Higher-Order Logic}}.
\newblock Number 2283 in LNCS. Springer, 2002.

\bibitem{FormalTheologyRepository}
B.~Woltzenlogel Paleo and C.~Benzm\"uller.
\newblock Formal theology repository
  (\url{https://github.com/FormalTheology/GoedelGod}).

\bibitem{ScottNotes}
D.~Scott.
\newblock {\em Appendix B. Notes in Dana Scott's Hand}, pages 145--146.
\newblock In  \cite{sobel2004logic}, 2004.

\bibitem{sobel2004logic}
J.H. Sobel.
\newblock {\em Logic and Theism: Arguments for and Against Beliefs in God}.
\newblock Cambridge U. Press, 2004.

\bibitem{J22}
G.~Sutcliffe and C.~Benzm{\"u}ller.
\newblock Automated reasoning in higher-order logic using the {TPTP THF}
  infrastructure.
\newblock {\em Journal of Formalized Reasoning}, 3(1):1--27, 2010.

\end{thebibliography}

>>>>

\bigskip

\noindent
\textbf{Update (16/08/2017):} The abstract below, uploaded to arXiv on 21/08/2013, was the first communication of the computer-assisted formalization of G\"odel's ontological proof. Since then, the following longer papers have been published: \cite{B39,B40,B45,B47,B49,B52,B56,B57,B60,B61,B62,B63,B64,B65,B66}.

\bigskip
\bigskip

@@

%\footnotesize
\bibliographystyle{plain}
\bibliography{Bibliography}
% \begin{thebibliography}{10}

% \bibitem{Adams}
% R.M. Adams.
% \newblock Introductory note to *1970.
% \newblock In {\em {Kurt G\"odel: Collected Works Vol. 3: Unpublished Essays and
%   Letters}}. Oxford University Press, 1995.

% \bibitem{AndersonGettings}
% A.C. Anderson and M.~Gettings.
% \newblock G\"odel ontological proof revisited.
% \newblock In {\em {G\"odel'96: Logical Foundations of Mathematics, Computer
%   Science, and Physics: Lecture Notes in Logic 6}}. {Springer}, 1996.

% \bibitem{B9}
% C.~Benzm{\"u}ller and L.C. Paulson.
% \newblock Exploring properties of normal multimodal logics in simple type
%   theory with {LEO-II}.
% \newblock In {\em {Festschrift in Honor of {Peter B. Andrews} on His 70th
%   Birthday}}, pages 386--406. College Publications.

% \bibitem{J23}
% C.~Benzm{\"u}ller and L.C. Paulson.
% \newblock Quantified multimodal logics in simple type theory.
% \newblock {\em Logica Universalis (Special Issue on Multimodal Logics)},
%   7(1):7--20, 2013.

% \bibitem{LEO-II}
% C.~Benzm{\"u}ller, F.~Theiss, L.~Paulson, and A.~Fietzke.
% \newblock {LEO-II} - a cooperative automatic theorem prover for higher-order
%   logic.
% \newblock In {\em Proc. of IJCAR 2008}, volume 5195 of {\em LNAI}, pages
%   162--170. Springer, 2008.

% \bibitem{Coq}
% Y.~Bertot and P.~Casteran.
% \newblock {\em {Interactive Theorem Proving and Program Development}}.
% \newblock Springer, 2004.

% \bibitem{Sledgehammer}
% J.C. Blanchette, S.~B\"ohme, and L.C. Paulson.
% \newblock Extending {Sledgehammer} with {SMT} solvers.
% \newblock {\em Journal of Automated Reasoning}, 51(1):109--128, 2013.

% \bibitem{Nitpick}
% J.C. Blanchette and T.~Nipkow.
% \newblock Nitpick: A counterexample generator for higher-order logic based on a
%   relational model finder.
% \newblock In {\em Proc. of ITP 2010}, number 6172 in LNCS, pages 131--146.
%   Springer, 2010.

% \bibitem{Satallax}
% C.E. Brown.
% \newblock Satallax: An automated higher-order prover.
% \newblock In {\em Proc. of IJCAR 2012}, number 7364 in LNAI, pages 111 -- 117.
%   Springer, 2012.

% \bibitem{ContemporaryBibliography}
% R.~Corazzon.
% \newblock Contemporary bibligraphy on the ontological proof
%   (\url{http://www.ontology.co/biblio/ontological-proof-contemporary-biblio.htm}).

% \bibitem{Fitting}
% M.~Fitting.
% \newblock {\em {Types, Tableaux and G\"odel's God}}.
% \newblock Kluver Academic Press, 2002.

% \bibitem{Goedel1970}
% K.~G\"odel.
% \newblock Ontological proof.
% \newblock In {\em {Kurt G\"odel: Collected Works Vol. 3: Unpublished Essays and
%   Letters}}. Oxford University Press, 1970.

% \bibitem{GoedelNotes}
% K.~G\"odel.
% \newblock {\em Appendix A. Notes in Kurt G\"odel's Hand}, pages 144--145.
% \newblock In  \cite{sobel2004logic}, 2004.

% \bibitem{Hazen}
% A.P. Hazen.
% \newblock On g\"odel's ontological proof.
% \newblock {\em Australasian Journal of Philosophy}, 76:361--377, 1998.

% \bibitem{Hurd03first-orderproof}
% J.~Hurd.
% \newblock First-order proof tactics in higher-order logic theorem provers.
% \newblock In {\em Design and Application of Strategies/Tactics in Higher Order
%   Logics, NASA Tech. Rep. NASA/CP-2003-212448}, 2003.

% \bibitem{Isabelle}
% T.~Nipkow, L.C. Paulson, and M.~Wenzel.
% \newblock {\em {Isabelle/HOL: A Proof Assistant for Higher-Order Logic}}.
% \newblock Number 2283 in LNCS. Springer, 2002.

% \bibitem{FormalTheologyRepository}
% B.~Woltzenlogel Paleo and C.~Benzm\"uller.
% \newblock Formal theology repository
%   (\url{https://github.com/FormalTheology/GoedelGod}).

% \bibitem{ScottNotes}
% D.~Scott.
% \newblock {\em Appendix B. Notes in Dana Scott's Hand}, pages 145--146.
% \newblock In  \cite{sobel2004logic}, 2004.

% \bibitem{sobel2004logic}
% J.H. Sobel.
% \newblock {\em Logic and Theism: Arguments for and Against Beliefs in God}.
% \newblock Cambridge U. Press, 2004.

% \bibitem{J22}
% G.~Sutcliffe and C.~Benzm{\"u}ller.
% \newblock Automated reasoning in higher-order logic using the {TPTP THF}
%   infrastructure.
% \newblock {\em Journal of Formalized Reasoning}, 3(1):1--27, 2010.

% \end{thebibliography}
